%------------------------
% Document Class and Packages
%------------------------
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{pdfpages}
\usepackage[normalem]{ulem}
\usepackage{fontawesome5}
\usepackage{array}
\input{glyphtounicode}



%------------------------
% Formatting Commands
%------------------------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{4.08003pt} % Set the footskip to avoid fancyhdr error
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Inline list formatting
\newlist{inlineitemize}{itemize*}{1}
\setlist[inlineitemize]{label=\textbullet}

% Ensure that pdf is machine readable/ATS parsable
\pdfgentounicode=1

%------------------------
% Custom commands
%------------------------
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSkillItem}[3]{
  \item\small{
    \textbf{#1 - \textit{#2}}{: #3 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[2]{
  \resumeItem{#1}{#2}\vspace{-4pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-5pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-10pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}

  \textbf{\href{https://github.com/CoenMeintjes}{\Large Coen Meintjes}} & Email : \href{mailto:chmeintjes@gmail.com}{chmeintjes@gmail.com}\\
  \href{https://github.com/CoenMeintjes/}{https://github.com/CoenMeintjes} & Mobile : \href{tel:+27721193849}{+27-72-119-3849} \\
  
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}

Business Intelligence Analyst currently driving data solutions at Sweepsouth, leveraging SQL, Python, Sisense and automation tools to deliver actionable insights that optimise operations and fuel strategic growth. Expert in translating stakeholder needs into impactful BI tools. Wins at Sweepsouth include the development of a suite of dashboards to track the launch of new product verticals while also enabling operations to reduce lost sales by 91\% YoY through targeted analytics and automation. Committed to transforming data into strategic wins for business success.

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{http://sweepsouth.com}{Sweepsouth}}{Cape Town, South Africa (Hybrid)}
      {BI and Data Analytics: Leveraging Data to Drive Actionable Insight.}{Sep. 2024 - present}
      
      \resumeItemListStart
        \resumeItem{Advanced Data Analytics}
          {Utilised advanced data analytics with SQL, Python, Sisense and Metabase to drive operational and strategic decisions, contributing to key company milestones in FY25.}
        \resumeItem{Supply Team Automation \& Optimisation}
          {Enabled the Supply Team to reduce lost sales due to supply shortages by 91\% (from 1,595 in January to 143 in March) with insights from lost sales dashboards, automated early notification systems and improving worker job matching via operating area analysis.}
        \resumeItem{Product \& Engineering Support}
          {Supported the Product \& Engineering Team in launching four new multi-service verticals within two months, increasing new customer acquisitions by 10\% and AVOS by 23\% (R475 vs. R385). Closely collaborated with engineering to enhance data collection enabling data-driven product development.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{http://dataorbis.com}{DataOrbis}}{Cape Town, South Africa (Hybrid)}
      {Data Visualisation Developer: Reporting on EPOS data to FMCG leaders.}{Aug. 2023 - Aug. 2024}
    
      \resumeItemListStart
        \resumeItem{Monthly, Weekly and Daily Report Delivery}
          {Worked in collaboration with the delivery team responsible for the successful delivery of EPOS data reports to clients on a periodic basis.}
        \resumeItem{Custom Report Development}
          {Worked closely with clients and account managers to develop customised reporting products that address unique data insight requirements.}
        \resumeItem{Data Checking and Troubleshooting}
          {Responsible for ensuring data integrity prior to client delivery. Acted as first point of contact for troubleshooting data errors and discrepancies in reports.}
        \resumeItem{Pyramid Analytics API integration}
          {Led the development of an automated daily report status notification that streamlines visualisation developer efficiency and creates line of sight for managers and team members.}
        \resumeItem{Automation and Innovation}
          {Avid contributor to internal automation and innovation initiatives. Led automation forum discussions on optimisation in the data visualisation space. Contributed to the development of a centralised client and resource allocation database. Worked on optimising daily report refresh schedules through utilising Python and the Pyramid API integration.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{http://irx.exchange/metals-gold}{Investor Relations Exchange}}{Cape Town, South Africa (remote)}
      {Data Analyst: Gained practical data experience by assisting a start-up.}{Feb. 2023 - Aug. 2023 (adhoc)}
      
      \resumeItemListStart
        \resumeItem{Dashboard Development}
          {Collaborated with the founder to strategise and develop financial data visualisations that would enhance market analysis capabilities for investors.}
        \resumeItem{Data Pipeline/ETL}
          {Streamlined data analysis by connecting to JSON API data feeds, enabling seamless data loading, transformation, and access to diverse datasets. Automated the data updating process to ensure up-to-date information for analysis.}
        \resumeItem{Dashboard Construction}
          { Created interactive Power BI dashboards for financial market analysis, enabling data-driven decision-making. Implemented DAX expressions to enhance data visualizations and help investors to derive valuable insights.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{http://purestructuretrading.com/education}{Pure Structure Trading }}{Kapolei, HI, USA (remote)}
      {Analytics Analyst: Analysis experience gained while working as web developer.}{Oct. 2020 - Aug. 2023 (contract)}
      
      \resumeItemListStart
        \resumeItem{Monthly Analytics Reporting}
          {Utilized Looker and Excel to analyse website, YouTube, and newsletter metrics, providing actionable insights and recommendations. Contributed to the longevity of a top-performing YouTube videos through content recommendations}
        \resumeItem{Web Development}
          {Leveraged a mix of theme templates and custom CSS to develop and maintain the company website on WordPress, driving business promotion, educational program sales, and content delivery.}
        \resumeItem{Workflow Automation}
          {Streamlined workflows and reduced manual efforts through the integration of tools like MemberPress and Zapier, automating tasks related to membership management, content distribution, and communication.}
        \resumeItem{Content Publishing}
          {Created and published finance and trading-related web content and newsletters, leveraging technical market analysis to deliver valuable market insights to subscribers.}
      \resumeItemListEnd

    \resumeSubheading
      {Self-Employed}{Cape Town, South Africa}
      {Market Analyst: Leveraged technical market analysis to manage private fund.}{May. 2019 - Jan 2023}
      
      \resumeItemListStart
        \resumeItem{Strategy \& Systems Development}
          {Devised and implemented analysis-driven trading strategies to capitalise on opportunities in the US Equity and WTI Crude Oil Futures Markets. Best-performing strategy achieved a 43\% win rate with 1.8:1 risk-reward ratio over 163 live trades.}
        \resumeItem{Data Management \& Performance Analysis}
          {Implemented robust data capturing systems and conducted regular performance analysis to refine strategic approaches and improve the decision-making processes.}
        \resumeItem{Algorithmic Trading}
          {Streamlined operations by developing Python-based quantitative systems, automating manual strategies to enhance efficiency, minimize human error, and optimize trade execution.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://tararokpacentre.co.za/about-tikologo/}{Tara Rokpa Centre}}{Groot Marico, South Africa}
      {Project Director - Tikologo Permaculture Project}{Jan. 2014 - Dec. 2019}
      
      \resumeItemListStart
        \resumeItem{Project Design and Implementation}
          {Directed the master planning and design of a 30ha regenerative agriculture and education site encompassing land-use designation, water security planning, crop planning, and infrastructure development. Effectively executed the project, resulting in an operational demonstration site still fostering sustainable agricultural practices and environmental education.}
        \resumeItem{Fundraising and Grant Management}
          {Secured ZAR 1.1 million in project funding from international donors between 2017-2019. Effectively managed the allocated funds, ensuring proper allocation, timely payments, and comprehensive financial reporting.}
        \resumeItem{Team Leader and Project Coordination}
          {Led a team of seven in the construction of an earth building while cultivating a collaborative and motivated work environment. Effectively guided the team to complete a residence which stands as a prominent model for local sustainable construction practices. Provided mentorship, training, and support to ensure exceptional workmanship and overall project success.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%--------TECHNICAL SKILLS------------
% \section{Technical Skills}

%   \resumeSubHeadingListStart

%     \resumeSubheading{Programming}{}
%     {Skilled in programming with a focus on Python and SQL. Experience in Git and GitHub for version control.}{}
%     \resumeItemListStart
%       \resumeSkillItem{Python}{2 yrs}{Skilled in data discovery, structuring, cleaning, joining and validation. Skilled in exploratory data analysis employing Pandas, Numpy, Matplotlib, Seaborn}
%       \resumeSkillItem{SQL}{2 yrs}{Proficient in modelling, creating and querying SQL databases using SQLite, PostgreSQL and Python}
%       \resumeSkillItem{Git}{1 yrs}{Experienced in using Git and GitHub for personal projects and portfolio}
%     \resumeItemListEnd
    
%     \resumeSubheading{Data Visualization and Tools}{}
%     {Proficient in utilizing the following tools to effectively communicate data insights:}{}
%     \resumeItemListStart
%       \resumeSkillItem{Pyramid Analytics}{1 yrs}{Professional experience developing and maintaining live dashboards reporting on retail data for Global FMCG clients.}
%       \resumeSkillItem{Power BI}{0.5 yrs}{Practical experience in building dashboards for financial market analysis through work with Investor Relations Exchange.}
%       \resumeSkillItem{Tableau}{0.5 yrs}{Utilized Tableau as part of the Google Advanced Data Analytics Certificate program.}
%       \resumeSkillItem{Excel}{6 yrs}{Proficient in utilizing formulas, performing data cleaning and structuring, creating pivot tables, indexing and utilizing various other functionalities.}
%       \resumeSkillItem{Looker Studio}{2 yrs}{Utilized Looker Studio to visualize Google Analytics and YouTube metrics during analytics role with Pure Structure Trading.}
%     \resumeItemListEnd
    
%     \resumeSubheading{Machine Learning}{}
%     {Obtained practical experience in the field through the completion of the Google Advanced Data Analytics Certificate.}{}
%     \resumeItemListStart
%       \resumeSkillItem{Supervised and Unsupervised Learning}{0.5 yrs}{Competent in all stages of the machine learning process, including planning, data preparation, model construction, tuning, and reporting. Proficient in a variety of techniques: Regression, Naive Bayes, K-means, Random Forest and Gradient Boosting.}
%       \resumeSkillItem{Machine Learning Software}{0.5 yrs}{Proficient in utilizing Python for machine learning tasks. Gained practical experience with popular data science packages including Scikit-learn, Statsmodels, and XGBoost.}
%     \resumeItemListEnd

%     \resumeSubheading{Cloud Platforms}{}
%     {Demonstrated practical expertise in leveraging cloud platforms for data analysis and management.}{}
%     \resumeItemListStart
%       \resumeSkillItem{Google Cloud Platform}{0.5 yrs}{Experience utilizing Google Cloud Platform APIs to parse Gmail data and retrieve YouTube metrics data for analysis}
%       \resumeSkillItem{Azure}{1 yrs}{Experience deploying function apps running Python code achieving automation of various tasks from daily status notification to automated trading models}
%     \resumeItemListEnd

%   \resumeSubHeadingListEnd

\section{Technical Skills}

  \resumeSubHeadingListStart

    \resumeSubheading{Programming}{}
    {Advanced skills in Python and SQL for data engineering and analytics, with Git for version control.}{}
    \resumeItemListStart
      \resumeSkillItem{Python}{2 yrs}{Expert in data pipelines, ETL processes, and analysis using Pandas, NumPy, SQLAlchemy, and BeautifulSoup. Automated workflows at SweepSouth and built PropScout’s real estate analysis tool.}
      \resumeSkillItem{SQL}{2 yrs}{Skilled in designing, querying, and optimizing PostgreSQL and SQLite databases for BI and data storage, powering dashboards and market analytics at SweepSouth and PropScout.}
      \resumeSkillItem{Git}{2 yrs}{Leveraged Git and GitHub for version control and collaboration across professional and personal projects, including PropScout.}
    \resumeItemListEnd
    
    \resumeSubheading{Data Visualization and BI Tools}{}
    {Proficient in delivering actionable insights through modern BI and visualization platforms.}{}
    \resumeItemListStart
      \resumeSkillItem{Sisense \& Metabase}{0.5 yrs}{Developed live dashboards at SweepSouth to track product verticals and operational KPIs, driving strategic decisions.}
      \resumeSkillItem{Streamlit}{1 yr}{Created dynamic PropScout dashboards with Plotly to visualize property investment metrics and market trends.}
      \resumeSkillItem{Power BI}{0.5 yrs}{Designed financial market dashboards for Investor Relations Exchange, improving stakeholder reporting.}
      \resumeSkillItem{Excel}{6 yrs}{Advanced skills in data cleaning, pivot tables, and formulas for financial and operational analysis.}
    \resumeItemListEnd
    
    \resumeSubheading{Machine Learning}{}
    {Practical experience from Google Advanced Data Analytics Certificate and project applications.}{}
    \resumeItemListStart
      \resumeSkillItem{Supervised and Unsupervised Learning}{0.5 yrs}{Applied regression, K-means, and Random Forest models to predict trends, with hands-on tuning and reporting.}
      \resumeSkillItem{ML Frameworks}{0.5 yrs}{Utilized Scikit-learn and Statsmodels in Python for predictive analytics and data exploration.}
    \resumeItemListEnd

    \resumeSubheading{Cloud and Automation}{}
    {Expertise in cloud platforms and automation for scalable data solutions.}{}
    \resumeItemListStart
      \resumeSkillItem{Google Cloud Platform}{1 yr}{Integrated Gmail API for automated data retrieval in PropScout and parsed YouTube metrics for prior analytics roles.}
      \resumeSkillItem{Azure}{1 yr}{Deployed Python function apps for task automation, including status notifications and trading models.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------------
\section{Projects}

  \resumeSubHeadingListStart 
    
    \resumeSubItem{\href{https://github.com/CoenMeintjes/PropScout}{PropScout}}
      {Developed a real-time property investment analysis tool using Python, integrating Google Gmail API for automated data retrieval, BeautifulSoup for web scraping, and SQLAlchemy with PostgreSQL (Supabase) for data modeling and storage. Built ETL pipelines to process listings into actionable insights, including market medians and investment metrics, visualized via Streamlit dashboards with Plotly. Managed version control and collaboration on GitHub.} \href{https://github.com/CoenMeintjes/PropScout}{\textit{(GitHub)}}

    \resumeSubItem{\href{https://github.com/CoenMeintjes/data_science_notebook_templates}{Data Science Notebook Collection}}
      {Enhanced productivity and efficiency by creating comprehensive Jupyter Notebook templates, optimizing personal workflows for exploratory data analysis (EDA), hypothesis testing, regression models, and machine learning tasks} \href{https://github.com/CoenMeintjes/data_science_notebook_templates}{\textit{(GitHub)}}

    \resumeSubItem{\href{https://github.com/CoenMeintjes/predicting_employee_churn_salifort_motors}{Predicting Employee Churn}}
      {Improved proficiency in performing thorough exploratory data analysis (EDA), building accurate predictive models, and extracting valuable insights from company datasets. Utilized Python, Pandas, Matplotlib, Seaborn, Scikit-Learn, and XGBoost.} \href{https://github.com/CoenMeintjes/predicting_employee_churn_salifort_motors}{\textit{(GitHub)}}
        
    \resumeSubItem{\href{https://github.com/CoenMeintjes/google_advanced_data_analytics_certificate_projects}{Google Advanced Data Analytics Projects}}
      {Demonstrates proficiency in diverse data analytics techniques, including data inspection, exploratory data analysis (EDA), statistical analysis, and machine learning. Utilized Python as the primary tool to execute tasks and extract meaningful insights from real-world scenarios.}\href{https://github.com/CoenMeintjes/google_advanced_data_analytics_certificate_projects}{\textit{(GitHub)}}

    % \resumeSubItem{\href{https://github.com/CoenMeintjes/analysing_south_african_property_markets}{Real Estate Market Analysis}}
    %   {Significantly improved proficiency in data discovery, structuring, cleaning, joining, and validation using public data sources. Leveraged Excel for comprehensive data analysis, visualization, and deriving valuable insights for property market analysis.} \href{https://github.com/CoenMeintjes/analysing_south_african_property_markets}{\textit{(GitHub)}}

    % \resumeSubItem{\href{https://github.com/CoenMeintjes/property_investment_analysis_framework}{Property Deal Analysis Framework}}
    %   {Expanded my analytical thinking and enhanced proficiency in Excel for data analysis by designing comprehensive frameworks for evaluating property investments and making data-driven decisions} \href{https://github.com/CoenMeintjes/property_investment_analysis_framework}{\textit{(GitHub)}}

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Coursera}{Online}
      {Completed a comprehensive variety of courses to acquire the skills of a data professional}{}
     
      \resumeItemListStart
        \resumeItem{\href{https://www.coursera.org/account/accomplishments/specialization/certificate/T7KKS2AB9TKF}{Google Advanced Data Analytics}}
          {Data Science Foundations, Python for Data, Exploratory Data Analysis, Statistical Analysis, Regression Analysis, Machine Learning. \href{https://www.coursera.org/account/accomplishments/specialization/certificate/T7KKS2AB9TKF}{\textit{(Verified certificate)}}}
        \resumeItem{\href{https://www.coursera.org/account/accomplishments/specialization/certificate/5U8MB5RW7KGU}{Python for Everybody}}
          {Data Structures, Accessing Web Data, JSON and XML, Networked Application Program Interfaces, Database design, SQL. \href{https://www.coursera.org/account/accomplishments/specialization/certificate/5U8MB5RW7KGU}{\textit{(Verified certificate)}}}
        \resumeItem{\href{https://www.coursera.org/account/accomplishments/specialization/certificate/T774YZFKVQ2Q}{Excel Skills for Business}} 
          {Excel Business Applications, Data Validation, Pivot Tables, Dashboard creation, Advanced Formula Use, Automation with VBA macros. \href{https://www.coursera.org/account/accomplishments/specialization/certificate/T774YZFKVQ2Q}{\textit{(Verified certificate)}}}
        \resumeItem{\href{https://www.coursera.org/account/accomplishments/certificate/JNFNEVCJ54D4}{Introduction to Git and GitHub}}
          {Version Control Systems, Using Git, Collaborating on GitHub, Reverting Changes, Creating Pull Requests.  \href{https://www.coursera.org/account/accomplishments/certificate/JNFNEVCJ54D4}{\textit{(Verified certificate)}}}
      \resumeItemListEnd

    \resumeSubheading
      {Apteros Trading}{Online}
      {Gained advanced skills in technical analysis of financial markets incl. 3 month mentorship.}{}

    \resumeSubheading
      {Tshwane University of Technology}{Pretoria, South Africa}
      {Bachelor of Technology Architecture: Professional}{Jan. 2008 -- Dec. 2011}

  \resumeSubHeadingListEnd
 


%-------------------------------------------
\end{document}
