%------------------------
% Document Class and Packages
%------------------------
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{pdfpages}
\usepackage[normalem]{ulem}
\usepackage{fontawesome5}
\usepackage{array}
\input{glyphtounicode}


%------------------------
% Formatting Commands
%------------------------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Inline list formatting
\newlist{inlineitemize}{itemize*}{1}
\setlist[inlineitemize]{label=\textbullet}

% Ensure that pdf is machine readable/ATS parsable
\pdfgentounicode=1

%------------------------
% Custom commands
%------------------------
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-10pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}

  \textbf{\href{https://github.com/CoenMeintjes}{\Large Coen Meintjes}} & Email : \href{mailto:chmeintjes@gmail.com}{chmeintjes@gmail.com}\\
  \href{https://github.com/CoenMeintjes/}{https://github.com/CoenMeintjes} & Mobile : \href{tel:+27721193849}{+27-72-119-3849} \\
  
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Coursera}{Online}
      {Completed a comprehensive variety of courses to acquire the skills of a data professional}{Jan. 2023 -- Jun. 2023}
     
      \resumeItemListStart
        \resumeItem{\href{https://www.coursera.org/account/accomplishments/specialization/certificate/T7KKS2AB9TKF}{Google Advanced Data Analytics}}
          {Data Science Foundations, Python for Data, Exploratory Data Analysis, Statistical Analysis, Regression Analysis, Machine Learning. \href{https://www.coursera.org/account/accomplishments/specialization/certificate/T7KKS2AB9TKF}{\textit{(Verified certificate)}}}
        \resumeItem{\href{https://www.coursera.org/account/accomplishments/specialization/certificate/5U8MB5RW7KGU}{Python for Everybody}}
          {Data Structures, Accessing Web Data, JSON \& XML, Networked Application Program Interfaces, Database design, SQL. \href{https://www.coursera.org/account/accomplishments/specialization/certificate/5U8MB5RW7KGU}{\textit{(Verified certificate)}}}
        \resumeItem{\href{https://www.coursera.org/account/accomplishments/specialization/certificate/T774YZFKVQ2Q}{Excel Skills for Business}} 
          {Excel Business Applications, Data Validation, Pivot Tables, Dashboard creation, Advanced Formula Use, Automation with VBA macros. \href{https://www.coursera.org/account/accomplishments/specialization/certificate/T774YZFKVQ2Q}{\textit{(Verified certificate)}}}
        \resumeItem{\href{https://www.coursera.org/account/accomplishments/certificate/JNFNEVCJ54D4}{Introduction to Git \& GitHub}}
          {Version Control Systems, Using Git, Collaborating on GitHub, Reverting Changes, Creating Pull Requests.  \href{https://www.coursera.org/account/accomplishments/certificate/JNFNEVCJ54D4}{\textit{(Verified certificate)}}}
      \resumeItemListEnd

    \resumeSubheading
      {Apteros Trading}{Online}
      {Gained advanced skills in technical analysis of financial markets incl. 3 month mentorship.}{Nov. 2021 -- Sep. 2022}

    % \resumeSubheading
    %   {Auroville Earth Institute}{Tamil Nadu, India}
    %   {Trained in Earthen Architecture Design and Construction}{Feb. 2016}

    % \resumeSubheading
    %   {Permaculture Research Institute}{Online}
    %   {Completed Permaculture Design Certificate acquiring skills in sustainable systems design.}{Jan. 2015 -- Aug. 2015}

    \resumeSubheading
      {Tshwane University of Technology}{Pretoria, South Africa}
      {Bachelor of Technology Architecture: Professional}{Jan. 2008 -- Dec. 2011}

  \resumeSubHeadingListEnd

%--------TECHNICAL SKILLS------------
\section{Technical Skills}

  % \begin{inlineitemize}

  %   \item \textbf{Programming:} \small{Proficient in Python, Pandas, Numpy, Scikit-learn, Matplotlib, Seaborn, SQL, Git}
  %   \item \textbf{Data Visualization:} \small{Skilled with Tableau, Power BI, Excel, Looker}
  %   \item \textbf{Machine Learning:} \small{Experience in various techniques; linear and logistic regression, Naive Bayes, K-means, decision trees, random forest, gradient boosting.}
  %   \item \textbf{Statistical Analysis:} \small{Familiar with hypothesis testing, ancova, manova \& mancova}
  %   \item \textbf{Cloud Platforms:} \small{Familiar with GCP, Azure}
    
  % \end{inlineitemize}

  \resumeSubHeadingListStart

    \resumeSubItem{Programming}
      {Proficient in Python, SQL, Pandas, Numpy, Scikit-learn, Matplotlib, Seaborn, Git} 
    \resumeSubItem{Data Visualization}
      {Skilled with Tableau, Power BI, Excel, Looker Studio} 
    \resumeSubItem{Machine Learning}
      {Experience with regression, Naive Bayes, K-means, random forest, gradient boosting.}
    \resumeSubItem{Statistical Analysis}
      {Familiar with hypothesis testing, ancova, manova \& mancova}
    \resumeSubItem{Cloud Platforms}
      {Familiar with GCP(APIs)}

  \resumeSubHeadingListEnd
  

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{http://irx.exchange/metals-gold}{Investor Relations Exchange}}{Cape Town, South Africa (remote)}
      {Freelance: ETL, Data Visualization, Product Development}{Feb. 2023 - present}
      
      \resumeItemListStart
        \resumeItem{ETL}
          {Enhanced data analysis processes by establishing connections to API data feeds in Power BI, enabling seamless data loading, transformation, and access to a diverse range of datasets.}
        \resumeItem{Power BI}
          {Created interactive dashboards for mutual fund and gold market charts driving better data-driven decision-making. Implemented DAX formulas to enhance data visualizations and insights.}
        \resumeItem{Product Development}
          {Collaborated with the client to strategise and develop financial data visualizations, leading to improved market analysis capabilities for investors.}
        \resumeItem{Data Updates}
          {Implemented an automated data update process, ensuring up-to-date information availability always ready for analysis.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{http://purestructuretrading.com/education}{Pure Structure Trading }}{Kapolei, HI, USA (remote)}
      {Contract: Data Analysis, Web Development, Content Creation}{Oct. 2020 - present}
      
      \resumeItemListStart
        \resumeItem{Data Analysis}
          {Analysed website, YouTube, and newsletter metrics using Looker and Excel, providing actionable insights and recommendations in reports. Enabled content recommendations that maintained the top-performing YT video for over two years.}
        \resumeItem{Web Development}
          {Developed and maintained company website on WordPress, driving business promotion, educational program sales, and delivery of learning material.}
        \resumeItem{Workflows}
          {Integrated plugins and tools like MemberPress and Zapier for membership management and workflow automation in content distribution and communication significantly reducing manual efforts.}
        \resumeItem{Content Production}
          {Published finance and trading related web content and newsletters leveraging technical market analysis to convey market insights to subscribers.}
      \resumeItemListEnd

    \resumeSubheading
      {Independent / Self-Employed}{Cape Town, South Africa}
      {Market Analyst, Strategy Development, Risk Management}{May. 2019 - Jan 2023}
      
      \resumeItemListStart
        \resumeItem{Strategy and Systems Development}
          {Devised and implemented analysis-driven trading strategies to capitalise on opportunities in the US Equity and WTI Crude Oil Futures Markets. Best-performing strategy achieved a 43\% win rate with 1.8:1 risk-reward ratio over 163 live market trades.}
        \resumeItem{Data Analysis}
          {Implemented comprehensive data capturing systems and maintained regular analysis of results. Leveraged insights to refine the strategic approaches and enhance decision-making processes.}
        \resumeItem{Algorithmic Trading}
          {Automated manual trading strategies by developing and implementing Python-based quantitative systems, enhancing efficiency and reducing the risk of human error in trade execution.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://tararokpacentre.co.za/about-tikologo/}{Tara Rokpa Center}}{Groot Marico, South Africa}
      {Project Director - Tikologo Permaculture Project}{Jan. 2014 - Dec. 2019}
      
      \resumeItemListStart
        \resumeItem{Project Design and Implementation}
          {Directed the master planning and design of a 30ha regenerative agriculture and education site encompassing land-use designation, water security planning, crop planning, and infrastructure development. Effectively executed the project, resulting in an operational demonstration site still fostering sustainable agricultural practices and environmental education.}
        \resumeItem{Fundraising and Grant Management}
          {Secured ZAR 1.1 million in project funding from international donors between 2017-2019. Effectively managed the allocated funds, ensuring proper allocation, timely payments, and comprehensive financial reporting.}
        \resumeItem{Team Leader and Project Coordination}
          {Led a team of seven in the construction of an earth building while cultivating a collaborative and motivated work environment. Effectively guided the team to complete a residence which stands as a prominent model for local sustainable construction practices. Provided mentorship, training, and support to ensure exceptional workmanship and overall project success.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubItem{\href{https://github.com/CoenMeintjes/PropScout}{PropScout}}
      {Exciting real estate investment app designed to empower investors and enable them to thrive in the dynamic property market. \href{https://github.com/CoenMeintjes/PropScout}{\textit{(GitHub)}}} 

    \resumeSubItem{\href{https://github.com/CoenMeintjes/analysing_south_african_property_markets}{Real Estate Market Analysis}}
      {Extensive property market analysis utilizing public data and data-driven approaches to identify potentially lucrative investment locations. \href{https://github.com/CoenMeintjes/analysing_south_african_property_markets}{\textit{(GitHub)}}}
    
    \resumeSubItem{\href{https://github.com/CoenMeintjes/property_investment_analysis_framework}{Property Deal Analysis Framework}}
      {Creating a standardized framework for evaluating property investments, enabling investors to make informed decisions and establish a consistent process for success. \href{https://github.com/CoenMeintjes/property_investment_analysis_framework}{\textit{(GitHub)}}}

    \resumeSubItem{\href{https://github.com/CoenMeintjes/predicting_employee_churn_salifort_motors}{Predicting Employee Churn}}
      {In-depth analysis of employee churn factors, including exploratory data analysis (EDA) and the development of predictive models to gain insights and forecast employee turnover. \href{https://github.com/CoenMeintjes/predicting_employee_churn_salifort_motors}{\textit{(GitHub)}}}
        
    \resumeSubItem{\href{https://github.com/CoenMeintjes/google_advanced_data_analytics_certificate_projects}{Google Advanced Data Analytics Projects}}
      {A collection of projects completed as part of the Google Advanced Data Analytics Certificate program, covering a wide range of topics including data inspection, exploratory data analysis (EDA), statistical analysis, and machine learning.\href{https://github.com/CoenMeintjes/google_advanced_data_analytics_certificate_projects}{\textit{(GitHub)}}}

    \resumeSubItem{\href{https://github.com/CoenMeintjes/data_science_notebook_templates}{Data Science Notebook Collection}}
      {A comprehensive collection of Jupyter Notebook templates for data science tasks, developed to improve workflow efficiency and cover a wide range of topics, including exploratory data analysis, hypothesis testing, regression models, and machine learning models. \href{https://github.com/CoenMeintjes/data_science_notebook_templates}{\textit{(GitHub)}}}

  \resumeSubHeadingListEnd


%--------TRANSFERABLE SKILLS------------
% \section{Transferable Skills}
%   \begin{inlineitemize}

%     \item \textbf{From Prior Work Experience:} \small{Project Management, Problem Solving, Project Documentation, Proposal \& Report Writing, Accounting \& Bookeeping, CAD Draughting.}
      
%   \end{inlineitemize}


%-------------------------------------------
\end{document}
